# covEstR

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/covEstR)](https://cran.r-project.org/package=covEstR)
[![CRAN_Downloads_Badge](http://cranlogs.r-pkg.org/badges/grand-total/covEstR)](http://cranlogs.r-pkg.org/badges/grand-total/covEstR)
[![codecov](https://codecov.io/gh/BenBarnard/covEstR/branch/master/graph/badge.svg)](https://codecov.io/gh/BenBarnard/covEstR)
[![Travis-CI Build Status](https://travis-ci.org/BenBarnard/covEstR.svg?branch=master)](https://travis-ci.org/BenBarnard/covEstR)


## Overview

`covEstR` is a covariance estimation suite. In creating other packages we found it useful to separate out our covariance estimation functions and maintain them somewhere else. This package works well with `hldr` and `covTestR`.

In developing `covEstR` we found it useful to have it play nice with the `tidyverse` suite of packages. At this point we have not thought of all the uses and combinations with these packages, so if you think of something not currently implemented please file a minimal reproducible example on GitHub.

Currently, we have written the Haff shrinkage estimator [1979](https://projecteuclid.org/euclid.aos/1176344845), but we are open to adding other covariance and precision matrix estimating functions. Note that our `cov()` function can return either covariance or precision matrices, depending on the function supplied to the `covEstR` argument. Please file an enhancement request on GitHub, and please include the following details in the request:

- Link to a published paper (or even a white paper) wherein the estimator is defined in simplest terms (matrix notation preferred)
- A quick example of how the estimator is useful (we will include this information in the function `help` file(s))

## Installation

You can install the latest development version from GitHub with

```{r}
if (packageVersion("devtools") < 1.6) {
  install.packages("devtools")
}
devtools::install_github("BenBarnard/covEstR")
```

If you encounter a clear bug, please file a minimal reproducible example on GitHub.

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(tidyverse)
library(covEstR)

# Total Precision
iris %>% select(-Species) %>% as.matrix %>% Haff_shrinkage

# Group Precision matrix estimates using our cov() function with the unbiased
#   estimator
cov(iris, group = "Species") %>% lapply(solve)

# Group Precision matrix estimates using our cov() function with the Haff
#   Shrinkage Estimator
cov(iris, group = "Species", covEst = Haff_shrinkage)
```
